---
title: "Applied biostatistics with R"
format:
  html:
    toc: false
---

{{< include _links.qmd >}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r timing, echo = FALSE}
start <- 1430
stop <- 1720
where <- "CRX-C323"
```

This is an undergraduate level class at the University of Ottawa taugh by [Julien Martin][lab_website]

When and where:

{{< include where.qmd >}}

# Course info

* [Lecture slides](lectures.qmd)
* [Practical manual][manual]
* [Syllabus](syllabus.qmd)


# Requirements

<!-- * Download and install [Git](https://git-scm.com/downloads). -->

* You will need a recent version of R (4.0.0 or highher)

* Install [`R`][cran] and your favourite R IDE [`RStudio`][rstudio_d] or [`VSCode`][vscode_d]

<!-- * Have Git, GitHub and RStudio talk to each other following [these guidelines (section 2.2.2 Configuration only)](https://inbo.github.io/git-course/course_rstudio.html#222_configuration). -->

<!-- * Install the following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line: -->

```{r eval = FALSE, echo = FALSE}
install.packages(c("tidyverse", "sf", "emo", "janitor", "palmerpenguins", "usethis", "lubridate"))
```

#### Corrections {-}

If you see mistakes or want to suggest changes, please [create an issue](https://github.com/biostats-uOttawa/bio4158_course/issues) on the source repository.

#### Reuse {-}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/biostats-uOttawa/bio4158_course/blob/master/LICENSE.md). 

